Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants\thanks{Supported by EPSRC grant EP/J012564/1, ERC project 280053 (CPROVER) and the H2020 FET OPEN 712689 SC$^2$.}

### 2017-05-04 cav2017/cav2017.tex
intro
Updated experimental section based on rebuttal
Added % for verification/synthesis time. Described bit width increase.
Removed obsolete comments.

For the majority of our benchmarks, we observe that the abstraction-based
back-end is faster than the basic multi-staged verification approach, and
finds one solution more (9) than the multi-staged back-end (8).  In direct
comparison, the abstraction-based approach is on average able to find a
solution in approximately 70\% of the time required using the multi-staged
back-end, and has a median run-time 1.4\,s, which is seven times smaller
than the multi-staged approach.  The two back-ends complement each other in
benchmark coverage and together solve all benchmarks in the set.

@@

\todo{Add the percentage of the total time taken by verification and synthesis.}

\todo{Discuss the number of abstraction refinements (inner loop, not the outer one)
  for the 2nd approach?
  Although, if it's always one, I'm not sure how interesting it is.. }
\vskip -0.5cm
The median run-time for our benchmark set is 9.4\,s.  Overall, the average
synthesis time amounts to approximately 15.6\,s.  We consider these times
short enough to be of practical use to control engineers, and thus affirm
EG1.

@@

The synthesized controllers are confirmed to be safe outside of our model
representation using MATLAB, achieving EG2.  A~link to the full
experimental environment, including scripts to reproduce the results, all
benchmarks and the tool, is provided in the
footnote as an Open Virtual Appliance
(OVA).\footnote{\url{www.cprover.org/DSSynth/controller-synthesis-cav-2017.tar.gz}}

@@

\textit{Benchmark selection:} We report an assessment of both our approaches
over a diverse set of real-world benchmarks.  Nevertheless, this set of
benchmarks is limited within the scope of this paper and the performance may
not generalize to other benchmarks.\\
%
\textit{Plant precision and discretization heuristic:} Our algorithm to
select suitable FWL word widths to model the plant behavior employs a
heuristic based on user-provided controller word-width specifications \blue{[explain how precision is increased as number of bits?]}.  For
the first approach, where we may need to increase the precision of the time
discretization, we select the time steps for the discretizations on a
similar basis.  This works sufficiently well for our benchmarks, but
performance may suffer in some cases, for example if the completeness
threshold is high.\\
%
\textit{Abstraction on other properties:} The performance gain from abstract
acceleration may not hold for more complex properties than safety, for
instance ``eventually reach and always remain in a given safe set''.

@@

The proof of Jury's criterion~\cite{fadali} relies on the fact that the relationship between states and
next states is defined by $x_{k+1} = (A_d - B_dK) x_k$, all computed
at infinite precision.  When we employ a FWL digital controller, the
operation becomes:
%
\begin{align*}
x_{k+1} &= A_d \cdot x_{k} -(\mathcal{F}_{\langle I_c,F_c \rangle}(K)\cdot\mathcal{F}_{\langle I_c,F_c \rangle}(x_{k})).  \\
x_{k+1} &= (A_d  - B_dK) \cdot x_k + B_dK\delta, 
%\\ x_{k+1}&=A_d x_{k} + B_du_{k}
\end{align*}
%
where $\delta$ is the maximum error that can be introduced by the FWL
controller in one step, i.e., by reading the states values once and
multiplying by $K$ once.  We derive the closed form expression for $x_n$ as
follows:
%
\begin{align*}
x_{1} &= (A_d  - B_dK)x_0 + B_dK\delta \\
x_{2} &= (A_d  - B_dK)((A_d  - B_dK)x_0 + B_dK\delta ) + B_dK\delta \\
      &=(A_d  - B_dK)^2x_0 + (A_d  - B_dK)B_dK\delta + B_dK\delta \\
%x_{3}  &=(A_d  - B_dK)^3x_0 + (A_d  - B_dK)^2B_dK\delta + (A_d  - B_dK)B_dK\delta + B_dK\delta\\
x_{n} &= (A_d  - B_dK)^nx_0 + (A_d  - B_dK)^{n-1}B_dK\delta + ... + (A_d  - B_dK)^1B_dK \delta + B_dK\delta \\
  &= (A_d - B_dK)^nx_0 + \sum_{i=0}^{i=n-1}(A_d - B_dK)^iB_dk\delta
\end{align*}

The definition of asymptotic stability is that the system converges to a
reference signal, in this case we use no reference signal so an
asymptotically stable system will converge to the origin.  We know that the
original system with an infinite-precision controller is stable, because we
have synthesized it to meet Jury's criterion.  Hence, $(A_d - B_dK)^n \cdot
x_0$ must converge to zero.

>>>>

For the majority of our benchmarks, we observe that the abstraction-based
back-end is faster than the basic multi-staged verification approach, and
finds one solution more (9) than the multi-staged back-end (8).  In direct
comparison, the abstraction-based approach is on average able to find a
solution in approximately 70\% of the time required using the multi-staged
back-end, and has a median run-time 1.4\,s, which is seven times smaller
than the multi-staged approach.  The two back-ends complement each other in
benchmark coverage and together solve all benchmarks in the set.  On average
our engine spent 52\% in the synthesis and 48\% in the verification phase.

@@

The median run-time for our benchmark set is 9.4\,s.  Overall, the average
synthesis time amounts to approximately 15.6\,s.  We consider these times
short enough to be of practical use to control engineers, and thus affirm
EG1.

@@

The synthesized controllers are confirmed to be safe outside of our model
representation using MATLAB, achieving EG2.  A~link to the full
experimental environment, including scripts to reproduce the results, all
benchmarks and the tool, is provided in the
footnote as an Open Virtual Appliance
(OVA).\footnote{\url{www.cprover.org/DSSynth/controller-synthesis-cav-2017.tar.gz}}
The provided experimental environment runs multiple discretisations for each
benchmark, but only lists the fastest as the result synthesis time.

@@

\textit{Benchmark selection:} We report an assessment of both our approaches
over a diverse set of real-world benchmarks.  Nevertheless, this set of
benchmarks is limited within the scope of this paper and the performance may
not generalize to other benchmarks.\\
%
\textit{Plant precision and discretization heuristic:} Our algorithm to
select suitable FWL word widths to model the plant behavior employs a
heuristic based on user-provided controller word-width specifications.
In order to be compliant with the CBMC type API, we increase the precision
by 8 bits at each step.
For the first approach, where we may need to increase the precision of the time
discretization, we select the time steps for the discretizations on a
similar basis.  This works sufficiently well for our benchmarks, but
performance may suffer in some cases, for example if the completeness
threshold is high.\\
%
\textit{Abstraction on other properties:} The performance gain from abstract
acceleration may not hold for more complex properties than safety, for
instance ``eventually reach and always remain in a given safe set''.

@@

The proof of Jury's criterion~\cite{fadali} relies on the fact that the relationship between states and
next states is defined by $x_{k+1} = (A_d - B_dK) x_k$, all computed
at infinite precision.  When we employ a FWL digital controller, the
operation becomes:
%
\begin{align*}
x_{k+1} &= A_d \cdot x_{k} -(\mathcal{F}_{\langle I_c,F_c \rangle}(K)\cdot\mathcal{F}_{\langle I_c,F_c \rangle}(x_{k})).  \\
x_{k+1} &= (A_d  - B_dK) \cdot x_k + B_dK\delta, 
%\\ x_{k+1}&=A_d x_{k} + B_du_{k}
\end{align*}
%
where $\delta$ is the maximum error that can be introduced by the FWL
controller in one step, i.e., by reading the states values once and
multiplying by $K$ once.  We derive the closed form expression for $x_n$ as
follows:
%
\begin{align*}
x_{1} &= (A_d  - B_dK)x_0 + B_dK\delta \\
x_{2} &= (A_d  - B_dK)((A_d  - B_dK)x_0 + B_dK\delta ) + B_dK\delta \\
      &=(A_d  - B_dK)^2x_0 + (A_d  - B_dK)B_dK\delta + B_dK\delta \\
%x_{3}  &=(A_d  - B_dK)^3x_0 + (A_d  - B_dK)^2B_dK\delta + (A_d  - B_dK)B_dK\delta + B_dK\delta\\
x_{n} &= (A_d  - B_dK)^nx_0 + (A_d  - B_dK)^{n-1}B_dK\delta + ... + (A_d  - B_dK)^1B_dK \delta + B_dK\delta \\
  &= (A_d - B_dK)^nx_0 + \sum_{i=0}^{i=n-1}(A_d - B_dK)^iB_dk\delta. 
\end{align*}

The definition of asymptotic stability is that the system converges to a
reference signal, in this case we use no reference signal so an
asymptotically stable system will converge to the origin.  We know that the
original system with an infinite-precision controller is stable, because we
have synthesized it to meet Jury's criterion.  Hence, $(A_d - B_dK)^n x_0$ 
must converge to zero.
